# Open Collaboration {#open-collaboration}

`Open collaboration` is any "system of innovation or production that relies on goal-oriented yet loosely coordinated participants who interact to create a product (or service) of economic value, which is made available to contributors and noncontributors alike."

It is prominently observed in open source software, or the creation of TEDx and Wikipedia.

- [x] goods of [economic value](#economic-value)
- [x] [open access](#open-access) to contribute and consume
- [x] [interaction](#interaction-exchange) and exchange 
- [x] purposeful yet [loosely coordinated](#purposeful) work

An annual conference dedicated to the research and practice of open collaboration is the International Symposium on Open Collaboration ([OpenSym](https://en.wikipedia.org/wiki/OpenSym)).

## Good economic value {#economic-value}

## Open Access {#open-access}


## Interaction and Exchange {#interaction-exchange}

### Simple, non-intrusive, secure communications

When you work with dozens of organizations employing hundreds of people, the last thing you want to get is endless cc: emails and bcc: emails that clutter your mailbox day and night. 

You also want to keep your private communications channels, like Whatsapp or Messgenger free from work messages. 

**Keybase** is our preferred tool to get in touch with us and ask questions, instead of emails, Whatsapp/Viber/Messenger/Telegram/Signal, that not everybody uses, and some people use for private matters only. *Keybase* is an open-source, free, privacy- and security-concerned alternative to *Slack* and similar chat-based collaboration tools. It is fully integrated with Zoom (which owns it recently) and Google Meet, so you can switch immediately to audio or video calls. Our observatories and Listen Local have their Keybase channels where you can interact with other curators and developers. [⇨ Annex / Collaboration tools / Keybase](#keybase) [⏯ keybase.io](#https://keybase.io/)

### Respectful, inclusive work environment

You must abide the [⏯ Contributor Covenant Code of Conduct](https://www.contributor-covenant.org/version/2/1/code_of_conduct/) (but *need not send* us proof) of pledging to make participation in our community a harassment-free experience for everyone, regardless of age, body size, visible or invisible disability, ethnicity, sex characteristics, gender identity and expression, level of experience, education, socio-economic status, nationality, personal appearance, race, caste, color, religion, or sexual identity and orientation. (See [translations](https://www.contributor-covenant.org/translations/) and the related [FAQ](https://www.contributor-covenant.org/faq/).)

```{r contributorcoventant}
add_graphics(file.path("png", "contributor_covenant.png"))
```


## Purposeful yet loosely coordinated work {#purposeful}

### Single file system that is secure and managed (overwrite) group conflicts

We use GitHub, because it meats EU FAIR and OPA requirements, and works in a far more interoperable (and affordable) way than *Microsoft Sharepoint*, or *Microsoft OneDrive*, and *Google Drive*, or *Drobox* for sharing file resources.

### One problem, one issue, one solution

### Simple task, milestone and deadline management

**Github**, a Git-based open source and free service (currently owned by Microsoft) is our tool for a very simple task tracking in a kanban-style. We use it in the [Digital Music Observatory](https://music.dataobservatory.eu/), in the [Open Collections Network](https://www.opencollections.net/) (used in Listen Local, WP2 Open Music Europe), because it complies with FAIR and OPA requirements (see earlier: [F](#findable)indable, [A](#accessible)ccessible, [I](#interoperability), [R](#reuse)reusable work), and it is free to use for most users.


```{r anywaykanban}
add_graphics(file.path("png", "anyway-kanban-gh.png"))
```
_Image credit: [Anyway Kanban](https://github.com/cat-street/anyway-kanban)_ 

For tracking tasks, you only need a web browser and an account on Github.  All project managers in our data observatories must have one, and curators are highly encouraged to join them, too. There are thousands of alternatives for *Github's kanban*, but we use it, because it integrates well with a far better product than i.e., *Microsoft Sharepoint*, or *Microsoft OneDrive*, and *Google Drive*, or *Drobox* for sharing file resources, such a clear and processed documents, spreadsheets, SPSS files, website elements, media files.

Because Github is a more advanced tool *for sharing files* than the aforementioned shared drives (it prevents the creation of conflicting versions of the same text, table or photograph), and because it integrates with a simple task management, it is also far more complicated to set-up/install and learn.  Github is a very simple for task management, to synchronize the file assets behind the tasks requires a bit of attention. But if you decide to go this way, you can build websites with us, blogs, publish journal articles, or even books. In scientific or open-source software cooperation using Github is fairly standard, so it will improve your ability to interact with colleagues. A curator does not need to use Github, unless he or she wants to cooperate on scientific outputs.  [⏯ github.com](https://github.com//)

- [x] If you have an existing Github account, please give us your [⏺ Github account ID](https://docs.github.com/en/get-started/signing-up-for-github/signing-up-for-a-new-github-account) as the preferred way of exchanging files. 
- [x] If you do not have one, please create a free account with a username that you would use professionally. 
- [ ] Please consider synching your files via Github with us after consulting our annex: [⏩ Annex / Collaboration tools / Github](#keybase).
- [ ] We can automate the issuing of DOI's to all your figures, code, text automatically via Zenodo and Github. 

## Bibliography management

```{r open-collab-zotero}
add_graphics(file.path("png", "zotero.png"))
```

- [x] We use the open source, free [Zotero](https://www.zotero.org/) research assistant. It can work with files created by Mendeley or OneNote. If you do not have a Zotero account, you should consider it after consulting our annex: [⏩ Annex / Collaboration tools / Zotero](#zotero)

- [ ] For publications, we export (and slightly modify) citation data to BibLatex, a text format that is required for most scientific journal/book Tex templates. Because no research assistant exports precisely the same way, manual adjustment is always required, so we keep up-to-date .bib collections on Github that are manually adjusted after exporting from Zotero, Mendeley, OneNote or downloaded directly from scientific libraries.
