--- 
title: "Contributors Guidebook for the Data Observatories and Open Collections"
author: "Daniel Antal"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::gitbook: default
  bookdown::word_document2:
    toc: false
    #reference_docx: templates/Horizon_Europe_template.docx
    language: English
  bookdown::epub_book: default
  bookdown::pdf_book:
    language: english
    toc: true
    tof: true
    includes:
      keep_tex: true
documentclass: book
bibliography: 
- book.bib
- packages.bib
- bib/opa.bib
- bib/opendata.bib
- bib/openscience.bib
biblio-style: apalike
classoption: openany, a4paper, oneside
lang: en
papersize: a4
fontsize: "fontsize=12pt"
linestretch: 1.1
urlcolor: blue
linkcolor: blue
geometry: "left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm"
github-repo: dataobservatory-eu/contributors
description: "Contributors Guidebook for the Data Observatories and Open Collections."
---

```{r setupknitr, include=FALSE}
knitr::opts_chunk$set(echo      = FALSE, 
                      message   = FALSE, 
                      warning   = FALSE,
                      out.width = '90%', 
                      fig.align = 'center')

library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(here)
here::here()
source(here("R", "html_caption.R"))
# Ellipsis: …

is_word_output <- ifelse (knitr::is_html_output()|knitr::is_latex_output(), FALSE, TRUE)
```

# Introduction {-}

::: {.rmdnote data-latex="{note}"}

Big data creates **inequalities**, because only the world’s biggest global corporations, best endowed universities and strongest governments can maintain long, well-designed, global data collection programs.

:::

This handbook is made for people working together in an [open collaboration](#open-collaboration) on the [Digital Music Observatory](https://music.dataobservatory.eu/) and its funded projects, [Listen Local Lithuania](https://lithuania.listen-local.net/), [Eviota](https://music.dataobservatory.eu/project/musiceviota/), [SurveyHarmonies](https://www.sinus-institut.de/en/sinus-institut/case-studies/surveyharmonies) and [Open Music Europe](https://music.dataobservatory.eu/project/openmusiceurope/); the connecting [Open Collection Network](https://www.opencollections.net/) and the [CCSI Data Observatory](https://ccsi.dataobservatory.eu/) and [Green Deal Data Observatory](https://greendeal.dataobservatory.eu/).

Get in [epub](https://contributors.dataobservatory.eu/observatory-contributors-handbook.epub) or [docx](https://contributors.dataobservatory.eu/observatory-contributors-handbook.docx) formats.

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
